SimWrapper, an open source web-based platform for interactive visualization of microsimulation outputs and transport data

### 2023-01-09 src/Paper.tex
submitted
camera-ready fixes

\author[a]{William Charlton}
\author[b]{Bhargava Sana}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth,height=2.8in]{images/fig-dashboard-1.png.pdf}
  \caption{Example dashboard showing (a) vehicle animation and point data, (b) point data aggregated into areas; (c) some basic chart summaries}
  \label{fig:chart1}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth,height=3in]{images/fig-dashboard-2.png.pdf}
  \caption{Example dashboard depicting network links and mode shift diagrams}
  \label{fig:chart2}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth,height=3.2in]{images/fig-komod-next.png.pdf}
  \caption{KoMo:Dnext project dashboard}
  \label{fig:chart3}
\end{figure}

>>>>

\author[a]{William Charlton*}
\author[b]{Bhargava Sana}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth,height=2.8in]{images/fig-dashboard-1.jpg}
  \caption{Example dashboard showing (a) vehicle animation and point data, (b) point data aggregated into areas; (c) some basic chart summaries}
  \label{fig:chart1}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth,height=3in]{images/fig-dashboard-2.jpg}
  \caption{Example dashboard depicting network link, X/Y point-based emissions, and mode shift diagrams}
  \label{fig:chart2}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth,height=3.2in]{images/fig-komod-next.jpg}
  \caption{KoMo:Dnext project dashboard}
  \label{fig:chart3}
\end{figure}
